\section*{Acknowledgements}
% Supervisors
First of all, I would like to thank my supervisors, Fran\c cois Richard and Roman P\"oschl, for the perfect PhD experience. 
% Enlightening 
During the three and a half years I have gained a lot of knowledge in Particle Physics due to the patient work of Fran\c cois and Roman. 
Thanks to their support I have participated in many international workshops and conferences, which have enormously increased my communication skills inside the scientific community. 
Their patience helped me to improve my English writing in scientific context, however, a careful reader may find mistakes associated to articles. 


% Jury 
I deeply appreciate the efforts of all jury members for reading carefully the manuscript, and spending their time to be present on my defense. Their practical comments helped me to improve significantly the text quality. 
Particularly, I would like to thank Achille Stocchi, as a director of LAL, for  recepting me as a PhD student in the laboratory.

I would like to thank to ILD and CALICE simulation groups for their prompt response on our requests for generation of simulated files, that became an essential part of the analysis. 

The PhD degree relies on all knowledge gained throughout more than a decade of intensive learning, therefore, this work is partially belong to all my teachers and professors from \'Ecole Polytechnique in France and DNU in Ukraine. 

% Administration Sylvie Prandt, Sylvie Teulet 
Je voudrais dire merci \'a mes collegues et l'administration du LAL, particularment \'a Sylvie Prandt et Sylvie Teulet pour résolution rapide de problèmes administratif et pour l'organisation du tout mes missions.

There would not any much progress without support of all friends, Rajiv and Mafalda, J\`er\'emy, Andrii Nagai, Andrii Usachov, Oleg, Leonid, Rita and Denys, and many wonderful people for their viable support and their help during the final steps in the Doctorate. Thank you. 
% Parents

Most important, I want to thank my parents, Igor and Iryna, for their constant attention and support through happy and hard moments of my life.  