\documentclass[a4paper, 12pt]{article}


\include{definitions}
\title{Hadronic showers in a highly granular silicon-tungsten calorimeter and production of bottom and top quarks at the ILC \\ Cascades hadroniques dans un calorimetre electromagn\'etique silicium-tungst\`ene hautement granulaire et production du quarks top et bottom \`a l'ILC}
\author{Sviatoslav BILOKIN\\Supervisor:  Roman P\"OSCHL}

\begin{document}
	
	\epigraph{Hodor!}{\textit{ - Hodor \\ A Song of Ice and Fire} \\George R. R. Martin}	\newpage
	
	\newpage
%\maketitle
%\include{TitlePage}

\renewcommand{\abstractname}{Abstract}
\begin{abstract}

This thesis presents studies for the International Linear Collider (ILC), a linear electron-positron collider with a nominal center-of-mass energy from 250\,GeV to 500\,GeV.

Data are analysed that were recorded with the physics prototype of the CALICE silicon-tungsten electromagnetic calorimeter (\ecal) prototype at FermiLab in 2008. During this thesis, a track-finding algorithm was developed, which finds secondary tracks in hadronic events recorded by the \ecalp. This algorithm reveals details of hadronic interactions in the detector volume and the results are compared with simulations based on the the \geant\ toolkit.

Indirect searches of New Physics require a high precision on the measurements of the \sm\ parameters. 
%Many theories of physics beyond the \sm\
Many \bsm\ theories, like extradimentional or composite models, imply modifications of electroweak couplings of the heavy quarks, top and bottom. The second part of the thesis is a full simulation study of vertexing algorithms in the ILD environment and the reconstruction of the b-quark charge. The b-quark charge reconstruction is essential for many physics channels at the ILC, particularly, for the $e^+e^-\to b\bar{b}$ and the $e^+e^-\to t\bar{t}$ channels.
The developed algorithm improves the b-quark charge reconstruction performance.

The b-quark charge reconstruction methods are applied to the analysis of the \ttbar\ production process. This allows to increase statistics for the top quark electroweak form factor estimation w.r.t an earlier study and thus to decrease corresponding statistical uncertainties.

The results of the detector study allow for an estimation of the ILC precision on the b-quark electroweak couplings and form factors. The ILC will be able to resolve the LEP anomaly in the \bbbar\ production process. The ILC precision on the right-handed $Z^0b\bar{b}$ coupling, a prime candidate for effects of new physics, is calculated to be at least 5 times better than the LEP experiments. 
\end{abstract}

\renewcommand{\abstractname}{Résumé}
\newpage\begin{abstract}
	Cette thèse présente études pour l'International Linear Collider (ILC), un collisionneur électron-positron linéaire avec une \'energie nominale dans le centre de masse de 250\,GeV à 500\,GeV.
	
	Les données analysées ont été enregistrées avec le 	 prototype physique CALICE d'un calorimétre \'electromagnetique silice-tungstène  (\ecal) à FermiLab en 2008. Au cours de cette thèse, un algorithme de recherche de traces a été développé, qui trouve des traces secondaires dans les événements hadroniques enregistrés par le prototype \ecal. Cet algorithme révèle des détails sur les interactions hadroniques dans le volume du détecteur et les résultats sont comparés avec des simulations basées sur le \geant\ toolkit.
	
	Les recherches indirectes de nouvelle physique nécessitent une haute précision sur les mesures des paramètres de Modèle Standard. Théories de la physique au-delà de Modèle Standard, comme theories de dimensions supplémentaires ou modeles composite, impliquent des modifications des couplages électrofaibles des quarks lourds, top et bottom. La deuxième partie de la thèse est une étude de simulation complète des algorithmes de vertexing dans l'environnement ILD et la reconstruction de la charge de quark b. La reconstruction de la charge du quark bottom est essentielle pour de nombreux canaux de physique à l'ILC, particulièrement, pour les reactions $e^+e^- \to b\bar{b}$ et $e^+e^- \to t\bar{t}$.
	L'algorithme développé améliore la performance de reconstruction de la charge du quark bottom.
	
	Les méthodes de reconstruction de la charge du quark bottom sont appliquées \`a l'analyse du mechanisme de production \ttbar. Cela permet d'augmenter la statistique pour l'estimation du facteur de forme électrofaible du quark top par rapport \`a une étude antérieure et donc de diminuer les incertitudes statistiques correspondantes.
	
	Les résultats de l'étude du détecteur permettent d'estimer la précision de l'ILC sur les couplages et les facteurs de forme  électro-faibles du quark bottom. L'ILC sera capable de résoudre l'anomalie du LEP dans le processus de production \bbbar. La précision de l'ILC sur le couplage droite $Z^0b\bar{b}$, un candidat majeur pour les effets de la nouvelle physique, est calculée et est au moins 5 fois mieux que celle des expériences de LEP.
	
\end{abstract}	
\newpage
\input{ack}
\newpage
\tableofcontents


\linenumbers
\newpage\part{Introduction}\label{PARTI}
\input{Introduction}
\newpage
\input{StandardModel}
\newpage
\input{ILC}
\newpage\part{Hadronic interactions in the Silicon-Tungsten Electromagnetic Calorimeter}\label{PARTII}
\input{ECAL/ECALAnalysis}
\newpage\part{Heavy quark production at the ILC}\label{PARTIII}
\input{ILD/ILDAnalysis}
\newpage
\input{Conclusions}
\newpage
\input{Appendices}
\newpage

\renewcommand\refname{References}



%\bibliography{can055}
\bibliography{mainbib}{}
%\bibliographystyle{plain}
\bibliographystyle{unsrt}
% \bibliographystyle{utphys_mod}
%\begin{thebibliography}{100} 
%\bibitem{bib:steinberger} A Brief history of the running of R(b) http://inspirehep.net/record/443353/
%\bibitem{bib:ILC} ILC TDR https://arxiv.org/pdf/1306.6327;
%\bibitem{bib:HiggsCms} ATLAS CMS HIGGS https://arxiv.org/abs/1207.7235
%\bibitem{bib:HiggsAtlas} https://arxiv.org/abs/1207.7214
%\bibitem{bib:HiggsAtlas2}  https://arxiv.org/abs/1408.5191v3
%\bibitem{bib:HiggsCms2} https://arxiv.org/abs/1508.07819
%\bibitem{bib:HiggsLhc2} https://arxiv.org/abs/1606.02266v2
%\bibitem{bib:alpha_s}  arXiv:0908.1135v2
%\bibitem{bib:Higgs_top} https://arxiv.org/pdf/1307.3536v4.pdf
%\bibitem{bib:AfbSMFit} https://arxiv.org/abs/1407.3792v1
%\bibitem{bib:PDGprop} http://pdg.lbl.gov/2016/AtomicNuclearProperties/
%\bibitem{bib:LumiUp}https://arxiv.org/pdf/1308.3726.pdf
%\bibitem{bib:Schmidt} https://arxiv.org/abs/hep-ph/9504434
%\bibitem{bib:TeVAfb} https://arxiv.org/pdf/1602.09015.pdf
%\bibitem{bib:TeVstop} https://arxiv.org/pdf/1405.2732.pdf
%\bibitem{bib:LEPTOP} https://arxiv.org/pdf/hep-ph/9411388.pdf
%\bibitem{bib:Han}https://arxiv.org/pdf/hep-ph/0508097.pdf
%\bibitem{bib:CMSttz2014} https://arxiv.org/pdf/1406.7830.pdf/
%\bibitem{bib:ILCTOP}https://arxiv.org/pdf/1505.06020.pdf
%\bibitem{bib:RSTOP}https://arxiv.org/abs/hep-ph/0610173
%\bibitem{bib:LCIOtrack}http://www-flc.desy.de/lcnotes/notes/LC-DET-2006-004.pdf
%\bibitem{bib:PDG}C. Patrignani et al. (Particle Data Group), Chin. Phys. C, 40, 100001 (2016).
%\bibitem{bib:LCFI} https://arxiv.org/abs/1506.08371
%\bibitem{bib:SLC} https://arxiv.org/pdf/hep-ex/9904016.pdf
%\bibitem{bib:HARP} http://harp-cdp.web.cern.ch/harp-cdp/dEdx.pdf
%\bibitem{bib:TopMass} https://arxiv.org/abs/1403.4427
%\bibitem{bib:Doublet} https://tel.archives-ouvertes.fr/tel-00657967/
%\bibitem{bib:H20}https://arxiv.org/pdf/1506.07830.pdf
%\bibitem{bib:LEPpuzzle}https://arxiv.org/pdf/hep-ph/0610173.pdf
%\end{thebibliography}

\end{document}
